---
title       : Central Limit Theorem
subtitle    : Develope Data Product
author      : Tan Woei Ming
job         : Coursera Course Project
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Draw Number

With a box of numbers 1 to 10, we randomly draw a number with replacement from the box and repeat for 500 times.

Make the frequency plot (histogram) of each number, the distribution is __NOT__ normal.

```{r echo=FALSE}
x<-runif(500, min=0, max=10)
par(mfrow=c(2,1))
hist(x, col = 'darkgray', border = 'white', main='histogram of random number',xlab='number',ylab='frequency',breaks=10,xlim=c(0,10))
```

--- 

## Draw N-sample of Number

With the same setting, we randomly draw (N=) 5 numbers (with replacement), then find the average. Repeat for 100 times. 

Make the frequency plot of each set of number average, the distribution become normal.

```{r echo=FALSE}
x<-runif(500, min=1, max=10)
x_agg<-colMeans(matrix(data=x,nrow=5))
par(mfrow=c(2,1))
hist(x_agg, col = 'darkgray', border = 'white', main='histogram of random number',xlab='number',ylab='frequency',breaks=10,xlim=c(0,10))
```

---

## Central Limit Theorem

Central Limit Theorem shows that the distribution of N-sample average becomes normal distribution, compared to individual drawing (NOT normal).

The theorem also has below properties:

1. The mean are the same as the population mean.

2. The standard deviation (sd) is 1/sqrt(N) of the population sd.

3. Normal distribution (Magic!!!)

For illustration apps:<https://twming.shinyapps.io/datascience-dataproducts/>

--- &radio
## Quiz

What is mean of N-sample draw?

1. twice of the population mean
2. _same as the population mean_
3. half of the population mean
4. no relation

*** .hint
It is the same set of number!

*** .explanation
Yes, Central Limit Theorem shows us they are the same as population mean!

